{\sf NodIO}, a framework for evolutionary algorithms in JavaScript: first results

### 2016-01-07 special-issue-ci/volunteer-clouds-ieee-ci-si-tr.tex
Title proposal

@@

As a volunteer based system, there are some issues that have to be addressed \cite{sarmenta2001volunteer,web:BOINC} :\begin{enumerate}
\item Volunteers are anonymous, only the Internet Protocol addresses (IP) sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer misbehaves in some way the provider cannot 
prosecute or discipline the volunteer. In the case of JavaScript,
this issue is aggravated because even if it is obfuscated, source code
and data is sent to clients. 
\item Participants must also trust the application provider, 
regarding invasion of privacy, the integrity of their devices, 
and intended application. 
\end{enumerate}

@@

After the initial experiments \cite{DBLP:journals/corr/GuervosG15}, we
realized that we needed to make some improvements. So, in order to
improve the number of cycles per user, we enhanced the 
basic architecture in several different aspects. One proposed improvement
involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Another was a small algorithmic
enhancement: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client. We called this instance of
the architecture NodIO-W$^2$. The other improvement was to 
use the Web Worker API as described next

>>>>

%(Mario) Maybe:  {\sf NodIO}, a JavaScript framework for volunteer-based evolutionary algorithms.

@@

As a volunteer based system, there are some issues that have to be addressed 
\cite{sarmenta2001volunteer,web:BOINC} :
\begin{enumerate}
\item Volunteers are anonymous, only the Internet Protocol addresses (IP) sent in 
each request is known.
\item As anonymous entities, volunteers are not accountable. 
If a volunteer misbehaves in some way the provider cannot 
prosecute or discipline the volunteer. In the case of JavaScript,
this issue is aggravated because even if it is obfuscated, source code
and data is sent to clients. 
\item Participants must also trust the application provider, 
regarding invasion of privacy, the integrity of their devices, 
and intended application. 
\end{enumerate}

@@

After the initial experiments \cite{DBLP:journals/corr/GuervosG15}, we
realized that we needed to make some improvements. So, in order to
improve the number of cycles per user, we enhanced the 
basic architecture in several different aspects. One proposed improvement
involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Another was a small algorithmic
enhancement: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client. We called this instance of
the architecture NodIO-W$^2$. The other improvement was to 
use the Web Worker API as described next.
